Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-12 inc/photocathode/este/este.tex
tweaks

\ref{fig:este-semicond} depicts the results obtained for GaSb and InSb photocathode materials under pulsed UV (261nm) laser irradiation using the same experimental technique employed for PAPE, 2PTE, and single-photon PE studies.
Both samples are cut from [100]-oriented polished wafers; the GaSb is undoped and the InSb is moderately $p$-type.
Prior studies~\cite{gobeli_photoelectric_1965} indicate that single-photon photoemission should not possible for either semiconductor --- the effective photoemission work functions (about 4.8eV for undoped GaSb and 4.89eV for $p$-type InSb (Fermi level pinned at valence band maximum)) being greater than the 4.75eV photon energy even when the 34meV Schottky barrier suppression due to the applied 8kV/cm DC field is included~\cite{dowell_quantum_2009}.
Nonetheless, for both zincblende semiconductors, significant laser-driven emission (more than expected for a single-photon field emission process) is observed with a yield nearly linearly proportional to the $\sim$4ps UV laser pulse energy.
Note that due to the surprisingly large yield, we repeated the measurements, this time replacing the the scintillator screen with a Faraday cup and repeating the laser energy sequence.
In this way, the yields for these photocathodes were measured directly and absolutely, unlike the results presented in the preceeding sections, for which relative measurements were sufficient.

>>>>

\ref{fig:este-semicond} depicts the results obtained for GaSb and InSb photocathode materials under pulsed UV (261nm) laser irradiation using the same experimental technique employed for PAPE, 2PTE, and single-photon PE studies.
Both samples are cut from [100]-oriented polished wafers; the GaSb is undoped and the InSb is moderately $p$-type.
Prior studies~\cite{gobeli_photoelectric_1965} indicate that single-photon photoemission should not possible for either semiconductor --- the effective photoemission work functions (about 4.8eV for undoped GaSb and 4.89eV for $p$-type InSb (Fermi level pinned at valence band maximum)) being greater than the 4.75eV photon energy even when the 34meV Schottky barrier suppression due to the applied 8kV/cm DC field is included~\cite{dowell_quantum_2009,berger_excited_2012}.
Nonetheless, for both zincblende semiconductors, significant laser-driven emission (more than expected for a single-photon field emission process) is observed with a yield nearly linearly proportional to the $\sim$4ps UV laser pulse energy.
Note that due to the surprisingly large yield, we repeated the measurements, this time replacing the the scintillator screen with a Faraday cup and repeating the laser energy sequence.
In this way, the yields for these photocathodes were measured directly and absolutely, unlike the results presented in the preceeding sections, for which relative measurements were sufficient.

### 2013-04-12 inc/photocathode/two_photon_thermionic/two_photon_thermionic.tex
tweaks

Two-photon assisted thermionic emission (2PTE) occurs when two photons provide nearly enough energy to emit a cold electron, and therefore a hotter electron, in the tail of the Fermi distribution, may have enough energy to be emitted~\cite{yen_thermally_1980}.
Of course this is even less efficient than direct two-photon photoemission, but as three-photon photoemission goes as $I^3$, 2PTE will still be the dominant photoemission mechanism.
For thermionic emission from electrons at a temperature $T_e$, the rms transverse momentum $\Delta p_{\smallT}$ is given by 
\begin{equation}
  \Delta p_{\smallT} = \sqrt{m k_B T_e} \,\text{,}
\end{equation}
where $k_B$ is the Boltzmann constant~\cite{dowell_quantum_2009,jensen_emittance_2010}.
Since a high laser intensity is required to drive 2PTE, the laser itself will heat the electrons, therefore, if the laser pulse duration is less than the thermalization time of the electron distribution, %TODO check this!
we expect the measured Fourier plane spot size to grow as incident laser pulse energy increases.

>>>>

Two-photon assisted thermionic emission (2PTE) occurs when two photons provide nearly enough energy to emit a cold electron, and therefore a hotter electron, in the tail of the Fermi distribution, may have enough energy to be emitted~\cite{yen_thermally_1980}.
Of course this is even less efficient than direct two-photon photoemission, but as three-photon photoemission goes as $I^3$, 2PTE will still be the dominant photoemission mechanism.
For thermionic emission from electrons at a temperature $T_e$, the rms transverse momentum $\Delta p_{\smallT}$ is given by 
\begin{equation}
  \Delta p_{\smallT} = \sqrt{m k_B T_e} \,\text{,}
\end{equation}
where $k_B$ is the Boltzmann constant~\cite{dowell_quantum_2009,jensen_emittance_2010}.
Since a high laser intensity is required to drive 2PTE, the laser itself will heat the electrons, therefore, we expect the measured Fourier plane spot size to grow as incident laser pulse energy increases, assuming that the laser pulse duration is less than the cooling time of the electron distribution so that the laser is only heating the electrons and not the lattice, which is true in this case.
